### 2014-04-15 doc/uist14/iteration3.tex
briefly refined the structure. wait until the study is done.

\section{Iteration 3: Head motion for disambiguation}
\label{sec:iteration-3:-head}

Though our {\em Valued IR} system is already performing well (with 3.71 seconds on average in a relative dense environment), we are only using head-orientation information during the {\em coarse selection} stage. In the {\em fine selection} part, we rely on the near-eye display. This has one fundamental problem -- we are projecting a high dimension distribution to a 1-dimension list. Therefore, it motivates us to explore using head orientation also during the {\em fine selection} stage.

@@

The sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of users' head. However, such absolute orientation cannot be directly used in any indoor environment because the user might change his location. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and sensors on Glass.

Before we describe how this new technique works. The relative orientation information -- {\em adjacent map} -- has to be learned before we can use it. Such a learning process can either be performed a prior, or through demonstration. \ben{need better elaboration here}.

@@

\ben{We then need evaluation results here, quantitative and qualitative.}

>>>>

\section{Iteration 3: Head motion for disambiguation}
\label{sec:iteration-3:-head}
\subsection{Problem Statement and Goal}
Though our {\em Valued IR} system is already performing well (with 3.71 seconds on average in a relative dense environment), head-orientation information is only used during the {\em coarse selection} stage. In the {\em fine selection} part, we rely on the near-eye display. This has two problems: First, we are projecting a high dimension distribution to a 1-dimension list. Second, this requires the user to switch their focus back and forth between the physical world and the near-eye display. Therefore, it motivates us design an approach that also utilize head orientation during the {\em fine selection} stage, and that there can be a more direct mapping between the user's gestures and target traversal.

@@

\subsection{Technique}
The sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of users' head. However, such absolute orientation cannot be directly used in any indoor environment because the user might change his location. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and sensors on Glass.

Before we describe how this new technique works. The relative orientation information -- {\em adjacent map} -- has to be learned before we can use it. Such a learning process can either be performed in advance, or through demonstration. \ben{need better elaboration here}.

@@

\subsection{Evaluation}
\ben{We then need evaluation results here, quantitative and qualitative.}
